Universal Anonymous Signatures

### 2022-05-24 prism-backend/research/gsac/transformations-uas.tex
Fixed typo.
Full proofs for security of CUASRing.

\begin{align}
  & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
  & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred)
  & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber \\
    \label{eq:uas-gsac-funcs}
\end{align}

@@

\subsection{Ring Signatures}
\label{ssec:uas-ring}

@@

To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
generic construction. This is due to the fact that the NP relation
$\NIZKRel_{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
issuers' public keys. This is a problem as, intuitively, the signer in a ring
signature is a sort of issuer for the ad hoc group. To hide the issuer, we
replace the NP relation in \secref{ssec:generic-construction-uas} with
$\NIZKRel_{\Sign-prv}$. We also use issuance function $\fissue^{\sring}$,
signature evaluation function $\feval^{\attrs}$, and opening function
$\finsp^0$. All of them are specified in \esref{eq:uas-ring-funcs}.

@@

Where \sring is some (arbitrary) ad hoc set containing the public keys of the
users that the signer wants to include in its ring. In $\NIZKRel_{\Sign-prv}$
the public keys of the issuers are now part of the witness in the NP relation,
which means that they will not be revealed in the proofs. Also, observe that, if
we let the attributes in a credential be public keys, $\fissue^{\sring}$ means
that a credential will be issued if all the public keys specified as attributes
to be included in the credential are part of the union of the ring and the
public key of the signer. To build $\feval^{\attrs}$, we define $\attrs(\cred)$
to be the function that returns all the attributes encoded in a credential.
Then, if the public key of the signer is included in the ring, $\feval^{\attrs}$
returns all the attributes in the credential (i.e., all the public keys in the
ring); otherwise, it aborts. Finally, let $\finsp^0$ disallows any
de-anonymization.

>>>>

\begin{align}
  & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
  & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred) \nonumber \\
  & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0)
    \label{eq:uas-gsac-funcs}
\end{align}

@@

\subsection{Ring Signatures}
\label{ssec:uas-ring}
\todo{This subsection needs much refinement.}

@@

\todo{Explain the following better...}
To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
generic construction. This is due to the fact that the NP relation
$\NIZKRel_{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
public key of the issuer of each credential used to produce the signatures.
This is a problem as, intuitively, the signer in a ring
signature is a sort of issuer for the ad hoc group. To hide the issuer, we
replace the NP relation in \secref{ssec:generic-construction-uas} with
$\NIZKRel_{\Sign-prv}$. We also use issuance function $\fissue^{\sring}$,
signature evaluation function $\feval^{\attrs}$, and opening function
$\finsp^0$. All of them are specified in \esref{eq:uas-ring-funcs}.

@@

Where $\usk \gets \isk$ for each issuer/user and, consequently 
\sring is some (arbitrary) ad hoc set containing the public keys of the
users (issuers) that the signer wants to include in its ring%
\footnote{Note that, implicitly, this conditions that the space of issuer public
  keys is a subset of \AttrSpace. If this is not the case ``by default'', this
  can be achieved via some appropriate mapping (e.g., an FDH or a XOF
  \needcite). That is, instead of having the ring be a set of {\ipk}s, we
  have the ring be a set of $F({\ipk}s)$, where $F$ is an appropriate mapping.
  For simplicity of exposition, we assume that the space of issuer public keys
  is compatible with \AttrSpace.}.
In $\NIZKRel_{\Sign-prv}$
the public keys of the issuers are now part of the witness in the NP relation,
which means that they will not be revealed in the proofs. Also, observe that, if
we let the attributes in a credential be public keys, $\fissue^{\sring}$ means
that a credential will be issued if all the public keys specified as attributes
to be included in the credential are part of the union of the ring and the
public key of the signer. To build $\feval^{\attrs}$, we define $\attrs(\cred)$
to be the function that returns all the attributes encoded in a credential.
Then, if the public key of the signer is included in the ring, $\feval^{\attrs}$
returns all the attributes in the credential (i.e., all the public keys in the
ring); otherwise, it aborts. Finally, let $\finsp^0$ disallows any
de-anonymization.
